Lesson 3
========================================================

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
list.files()

pf=read.csv('pseudo_facebook.tsv', sep='\t')
```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
#install.packages('ggplot2')
library(ggplot2)
```
```{r}
qplot(x=dob_day, data=pf)+
  scale_x_continuous(breaks=1:31)
```
```{r}
ggplot(aes(x = dob_day), data = pf) + 
  geom_histogram(binwidth = 1) + 
  scale_x_continuous(breaks = 1:31)
```

***

#### What are some things that you notice about this histogram?
Response:

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}
ggplot(aes(x = dob_day), data = pf) + 
  geom_histogram(binwidth = 1) + 
  scale_x_continuous(breaks = 1:31)+
  facet_wrap(~dob_month)
```

#### Let’s take another look at our plot. What stands out to you here?
Response:

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
ggplot(pf, aes(x=friend_count))+
  geom_histogram(binwidth=25)+
  scale_x_continuous(limits=c(0,1000), breaks=seq(0,1000,50))
```

#### How is this plot similar to Moira's first plot?
Response:

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}

```

### Exploring with Bin Width
Notes:

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))+
                   facet_wrap(~gender)
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}
qplot(x = friend_count, data = subset(pf, !is.na(gender)), binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))+
                   facet_wrap(~gender)
```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
tapply(pf$friend_count,pf$Gender,summary)
```

#### Who on average has more friends: men or women?
Response:

#### What's the difference between the median friend count for women and men?
Response:

#### Why would the median be a better measure than the mean?
Response:

***

### Tenure
Notes:

```{r Tenure}
ggplot(pf, aes(x=tenure/365))+
  geom_histogram(binwidth=1)
```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}

```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
ggplot(aes(x = tenure / 365), data = pf) + 
  geom_histogram(color = 'black', fill = '#F79420') + 
  scale_x_continuous(breaks = seq(1, 7, 1), limits = c(0, 7)) + 
  xlab('Number of years using Facebook') + 
  ylab('Number of users in sample')
```

***

### User Ages
Notes:

```{r User Ages}
str(pf$age)

```

#### What do you notice?
Response:

***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:

***

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}

install.packages('gridExtra') 
library(gridExtra) 
```
```{r}
p1=ggplot(pf, aes(x=pf$friend_count))+
  geom_histogram(binwidth=50)+
  scale_x_continuous(limits=c(0,1000), breaks=seq(0,1000,50))
p2=ggplot(pf, aes(x=log10(pf$friend_count+1)))+
  geom_histogram()
p4=p2=ggplot(pf, aes(x=pf$friend_count+1))+
  geom_histogram()+scale_x_log10()
p3=ggplot(pf, aes(x=sqrt(pf$friend_count)))+
  geom_histogram()

grid.arrange(p1,p2,p3,p4,nrow=4)

```

***


### Frequency Polygons

```{r Frequency Polygons}
ggplot(subset(pf,!is.na(pf$gender)),aes(x=friend_count, y = ..count../sum(..count..), color=gender))+
         geom_freqpoly(binwidth =10)+
         scale_x_continuous(limits=c(0,1000), breaks=seq(0,1000,50))
```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
by(pf$www_likes,pf$gender,sum)
ggplot(aes(x = www_likes), data = subset(pf, !is.na(gender))) + 
  geom_freqpoly(aes(color = gender)) + 
  scale_x_log10()
```


***

### Box Plots
Notes:

```{r Box Plots}
ggplot(subset(pf,!is.na(pf$gender)),aes(y=friend_count, x=gender))+
         geom_boxplot()+
        # scale_y_continuous(limits=c(0,1000)
        coord_cartesian(ylim=c(0,250))
```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}
ggplot(subset(pf,!is.na(pf$gender)),aes(y=friend_count, x=gender))+
         geom_boxplot()+
        # scale_y_continuous(limits=c(0,1000)
        coord_cartesian(ylim=c(0,1000))
```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}
ggplot(subset(pf,!is.na(pf$gender)),aes(y=friendships_initiated, x=gender))+
         geom_boxplot()+
        # +scale_y_continuous(limits=c(0,1000)
        coord_cartesian(ylim=c(0,250))

```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}
by(pf$friendships_initiated, pf$gender, mean)
```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}
summary(pf$mobile_likes)
mean(ifelse(pf$mobile_likes>0,1,0))
```

Response:

***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!